A Taxonomy of Twists of Supersymmetric Yang--Mills Theory -- Comments on Referee Report

### 2022-04-14 paper_journal_edits.tex
A few more corrections

\textbf{Dimension 8}
\begin{itemize}
 \item \emph{$\mc N=1$ holomorphic twist.} Super Yang--Mills theory in 8 dimensions admits three classes of twists.  The minimal twist, by a holomorphic (or, equivalently, pure) supercharge, is equivalent to a holomorphic version of the BF theory defined on a complex 4-fold.
 \item \emph{$\mc N=1$ intermediate twist.} The holomorphic twist admits a deformation to a twist by a rank 1 impure spinor \footnote{When we refer to the \emph{rank} of a supercharge we will always mean the rank as a tensor, for instance in the 8d $\mc N=8$ case supercharges live in a tensor product $S \otimes W$, where $S$ is an irreducible representation of $\spin(8)$ and $W$ is a two-dimensional auxiliary symplectic vector space.}. This theory is equivalent to a generalized version of the Chern--Simons theory defined on a product of a Calabi--Yau 3-fold and an oriented surface. Note that this theory is only $\ZZ/2\ZZ$-graded.
 \item \emph{$\mc N=1$ topological twist.} The holomorphic twist also admits a deformation to a topological twist defined on $\spin(7)$-manifolds. This theory is perturbatively trivial, in the sense that the classical BV complex is contractible. It was studied in \cite{AcharyaOLoughlinSpence,BaulieuKannoSinger}. The partition function of this theory counts $\spin(7)$-instantons modulo gauge \cite{Lewis,DonaldsonThomas,ReyesCarrion}. If we denote by $\Omega$ the Cayley 4-form on a $\spin(7)$-manifold $M$, then the classical solutions are given by principal $G_\RR$-bundles on $M$ (where $G_\RR$ is a compact Lie group) together with a connection $A$, such that its curvature $F_A$ satisfies the equation
\begin{equation} 
 F = \ast (\Omega\wedge F).
 \end{equation}
\end{itemize}

@@

\begin{remark}
The last condition $p^* S_N = S_M$ should be understood as an equality as local functionals or equivalently as follows. 
We recall that we can associate to the local functional $S_M$ an element of $\cO(\cE_{M,c}(M))$ where $\cE_{M,c}(M)$ is the space of compactly supported global sections of $E_M$ and similarly we can associate to the local functional $S_N$ an element of $\cO(\cE_{N,c}(N))$. 
Using the isomorphism $p^* E_N \cong E_M$, pulling back induces a map $p^* \colon \cO(\cE_{N,c}(N)) \to \cO(\cE_{M,c}(M))$ and we require $p^*S_N = S_M$ in $\cO(\cE_{M,c}(M))$.
\end{remark}

@@

Under the composition
\[\Omega^\bullet(V_\RR; \CC)\xto{\mr{Re}^*} \Omega^\bullet(V)\rightarrow \Omega^{0, \bullet}(V)\]
defined by pulling back forms along $\mr{Re}$ and projecting onto $(0,\bu)$-forms, the map $\Omega_V\wedge (-)\colon \Omega^{0, \bullet}_V \to \Omega^{{\rm dim}(V),\bu}_V \to \Omega^{\dim(V),\dim(V)}_V = {\rm Dens}_V$ given by projection onto the top component, reduces to the map $\Omega^{\bullet}(V_\RR;\CC)\rightarrow \Omega^{\dim(V)}_{V_\RR} = {\rm Dens}_{V_\RR}$ which also projects onto the top component. 
This shows that the BV pairings of the original and dimensionally reduced theory are compatible. 
\end{proof}

@@

Let $V_\RR$ be a finite-dimensional real vector space of dimension $n=\dim_\RR(V_\RR)$ equipped with an orientation and a nondegenerate symmetric bilinear form. Denote by $V=V_\RR\otimes_\RR\CC$ its complexification. Consider the Lie algebra $\so(V)$. Let us recall the following facts:
\begin{itemize}
\item If $n$ is odd, $\so(V)$ has a distinguished fundamental representation called the \defterm{spin} representation $S$.

@@

Let $Q\in\Sigma$ be a square-zero supercharge, which we will fix for the rest of this section. 
The image of $\Gamma(Q, -)\colon \Sigma\rightarrow V$ is a complex isotropic subspace $L\subset V$. Denote by $\sigma\colon V\rightarrow V$ the complex conjugation induced by the real structure $V = V_\RR\otimes_\RR\CC$. Since the bilinear form on $V_\RR$ is positive-definite, $L\cap \sigma(L) = 0$. In other words, $L$ defines a (linear) complex structure on $V_\RR$. Moreover, we may canonically identify $\sigma(L)\cong L^*$.

@@

The 4d $\cN=4$ super Yang--Mills theory is obtained by dimensional reduction from the 10d $\cN=(1, 0)$ super Yang--Mills. It admits $R$-symmetry group $G_R=\Spin(6; \CC)\cong \SL(4, \CC)$ under which $W \cong S_+^6$ is the positive six-dimensional semi-spin representation and $W^* \cong S_-^6$.

>>>>

\textbf{Dimension 8}
\begin{itemize}
 \item \emph{$\mc N=1$ holomorphic twist.} Super Yang--Mills theory in 8 dimensions admits three classes of twists.  The minimal twist, by a holomorphic (or, equivalently, pure) supercharge, is equivalent to a holomorphic version of the BF theory defined on a complex 4-fold.
 \item \emph{$\mc N=1$ intermediate twist.} The holomorphic twist admits a deformation to a twist by a rank 1 impure spinor \footnote{When we refer to the \emph{rank} of a supercharge we will always mean the rank as a tensor, for instance in the 8d $\mc N=1$ case supercharges live in a tensor product $S \otimes W$, where $S$ is an irreducible representation of $\spin(8)$ and $W$ is a two-dimensional auxiliary symplectic vector space.}. This theory is equivalent to a generalized version of the Chern--Simons theory defined on a product of a Calabi--Yau 3-fold and an oriented surface. Note that this theory is only $\ZZ/2\ZZ$-graded.
 \item \emph{$\mc N=1$ topological twist.} The holomorphic twist also admits a deformation to a topological twist defined on $\spin(7)$-manifolds. This theory is perturbatively trivial, in the sense that the classical BV complex is contractible. It was studied in \cite{AcharyaOLoughlinSpence,BaulieuKannoSinger}. The partition function of this theory counts $\spin(7)$-instantons modulo gauge \cite{Lewis,DonaldsonThomas,ReyesCarrion}. If we denote by $\Omega$ the Cayley 4-form on a $\spin(7)$-manifold $M$, then the classical solutions are given by principal $G_\RR$-bundles on $M$ (where $G_\RR$ is a compact Lie group) together with a connection $A$, such that its curvature $F_A$ satisfies the equation
\begin{equation} 
 F = \ast (\Omega\wedge F).
 \end{equation}
\end{itemize}

@@

\begin{remark}
The last condition $p^* S_N = S_M$ should be understood as an equality of local functionals or, equivalently, as follows. 
We recall that we can associate to the local functional $S_M$ an element of $\cO(\cE_{M,c}(M))$ where $\cE_{M,c}(M)$ is the space of compactly supported global sections of $E_M$ and similarly we can associate to the local functional $S_N$ an element of $\cO(\cE_{N,c}(N))$. 
Using the isomorphism $p^* E_N \cong E_M$, pulling back induces a map $p^* \colon \cO(\cE_{N,c}(N)) \to \cO(\cE_{M,c}(M))$ and we require $p^*S_N = S_M$ in $\cO(\cE_{M,c}(M))$.
\end{remark}

@@

Under the composition
\[\Omega^\bullet(V_\RR; \CC)\xto{\mr{Re}^*} \Omega^\bullet(V)\rightarrow \Omega^{0, \bullet}(V)\]
defined by pulling back forms along ${\rm Re}\colon V \to V_{\RR}$ and projecting onto $(0,\bu)$-forms, the map $\Omega_V\wedge (-)\colon \Omega^{0, \bullet}_V \to \Omega^{{\rm dim}(V),\bu}_V \to \Omega^{\dim(V),\dim(V)}_V = {\rm Dens}_V$ given by projection onto the top component, reduces to the map $\Omega^{\bullet}(V_\RR;\CC)\rightarrow \Omega^{\dim(V)}_{V_\RR} = {\rm Dens}_{V_\RR}$ which also projects onto the top component. 
This shows that the BV pairings of the original and dimensionally reduced theory are compatible. 
\end{proof}

@@

Let $V_\RR$ be a finite-dimensional real vector space of dimension $n=\dim_\RR(V_\RR)$ equipped with an orientation and a positive-definite nondegenerate symmetric bilinear form. Denote by $V=V_\RR\otimes_\RR\CC$ its complexification. Consider the Lie algebra $\so(V)$. Let us recall the following facts:
\begin{itemize}
\item If $n$ is odd, $\so(V)$ has a distinguished fundamental representation called the \defterm{spin} representation $S$.

@@

Let $Q\in\Sigma$ be a nonzero square-zero supercharge, which we will fix for the rest of this section. 
The image of $\Gamma(Q, -)\colon \Sigma\rightarrow V$ is a complex Lagrangian (i.e. maximal isotropic) subspace $L\subset V$. Denote by $\sigma\colon V\rightarrow V$ the complex conjugation induced by the real structure $V = V_\RR\otimes_\RR\CC$. Since the bilinear form on $V_\RR$ is positive-definite, $L\cap \sigma(L) = 0$. In other words, $L$ defines a (linear) complex structure on $V_\RR$. Moreover, we may canonically identify $\sigma(L)\cong L^*$.

@@

The 4d $\cN=4$ super Yang--Mills theory is obtained by dimensional reduction from the 10d $\cN=(1, 0)$ super Yang--Mills. It admits $R$-symmetry group $G_R=\Spin(6; \CC)\cong \SL(4, \CC)$ under which $W \cong S_+^6$ is the positive semi-spin representation of $\Spin(6; \CC)$ and $W^* \cong S_-^6$.

### 2022-04-14 twist_selecta_referee_comments.tex
A few more corrections

\begin{enumerate}
 \item Page 8: Added an explanatory comment.
 \item Page 18: \chris{I propose that the best thing to do here would be to add a longish remark on $\infty$-categories with some references, but reassuring the reader that no knowledge of details is needed to understand the content of the paper.}
 \item Page 20 points 1 and 2: Some further explanation was added for the notation here.
 \item Page 20 point 3: Added a remark, thank you.
 \item Page 27: Added an additional remark here to clarify the definition here.
 \brian{Maybe the issue is also with us calling this a BRST 'theory'? Perhaps less conflicting will be to refer to this as 'BRST data'. What do you think?} \chris{I don't think that's the issue, but maybe we should use a letter other than $\mathcal M$ for the formal moduli problem here.  Like maybe $\mathcal F$ for fields?}
 \item Page 29: Used $1/j$ for the root of the canonical bundle instead of $1/m$.
 \item Page 32: Clarified the condition $p^*S_N = S_M$ with a remark and fixed a small typo in the definition. \brian{Todo, mobius example. Not sure what they want.... Todo, category of vector bundles, I don't see what the category should have to do with issues of compactness.} \chris{He has an arrow pointing at the statement $p^*S_M = S_N$, so maybe the issue is with the way we think about action functionals.  Maybe we should use different notation to indicate that the local functional really refers to a Lagrangian density, so there's no problem defining it on something noncompact (and no need to integrate).}
 \item Page 34 point 1: The intended map here was the pullback along $\mr{Re} \colon V \to V_\RR$, corrected here. \chris{Todo, respond to the other part.}
 \item Page 34 point 2: The parameter $\eps$ in the given equivalence corresponds to $\d z$, where $z$ is a complex coordinate on the factor $\CC$.  Because this parameter has degree 1, it is formal and the issue indicated here does not arise.
 \item Page 35: Added some clarification to the notation here.
 \item Page 36: Yes, $Q_i$ and $\lambda$ are sections of the same thing, clarified this point. \chris{rest to respond to}
 \item Page 37: Added a clarifying sentence to the beginning of Section 2.1 about Euclidean signature. \brian{Todo: non associative stuff.}
 \item Page 38:
 \item Page 51: Thank you, reference added.
 \item Page 52: \chris{I talked to Brian about this, I'm not totally sure that I understand the objection.  Maybe the point is that the twisted theory can still admit real forms that could be thought of as twists of a real form of the supersymmetric theory, even if the corresponding real form didn't include a square-zero supercharge?} 
 \item Page 54: Added a reference for this claim to the relevant section of [ES].
 \item Page 56: This section was written confusingly, and we have corrected it.  Both $Q_+$ and $Q_-$ individually have stabilizers isomorphic to $\mr{SU}(4)$, and the intersection of these stabilizers is isomorphic to $\mr{SU}(3)$.
\end{enumerate}

>>>>

\begin{enumerate}
 \item Page 8: Added an explanatory comment.
 \item Page 18: \chris{I propose that the best thing to do here would be to add a longish remark on $\infty$-categories with some references, but reassuring the reader that no knowledge of details is needed to understand the content of the paper.}
 \pavel{Hmm. I would prefer not to add anything about $\infty$-categories as we are not really using them. Could be good to say that we use the equivalence as a black box: we \emph{define} FMPs as $L_\infty$ algebras. Like in Definition 1.6, how about we just give a definition ``an FMP is an $L_\infty$ algebra'' and add a remark after the definition that it is justified by the Lurie--Pridham result, but we will not be using it?}

 \item Page 20 points 1 and 2: Some further explanation was added for the notation here. \pavel{We define cotangent bundles etc of formal moduli problems, but then work with local formal moduli problems. The confusion arises because we never really defined what $T^*BL$ is when $L$ is a local $L_\infty$ algebra.}
 \item Page 20 point 3: Added a remark, thank you.
 \item Page 27: Added an additional remark here to clarify the definition.
 \brian{Maybe the issue is also with us calling this a BRST 'theory'? Perhaps less conflicting will be to refer to this as 'BRST data'. What do you think?} \chris{I don't think that's the issue, but maybe we should use a letter other than $\mathcal M$ for the formal moduli problem here.  Like maybe $\mathcal F$ for fields?}
 \pavel{Perhaps, we should just reply to the referee rather than add a remark? Agree about changing the letters though to clarify matters: the FMP he writes down is associated to BV fields, while here we have an extra data. If we change the letters, it will be easier to address the objection.}
 \item Page 29: Used $1/j$ for the root of the canonical bundle instead of $1/m$.
 \item Page 32: Clarified the condition $p^*S_N = S_M$ with a remark and fixed a small typo in the definition. \brian{Todo, mobius example. Not sure what they want.... Todo, category of vector bundles, I don't see what the category should have to do with issues of compactness.} \chris{He has an arrow pointing at the statement $p^*S_M = S_N$, so maybe the issue is with the way we think about action functionals.  Maybe we should use different notation to indicate that the local functional really refers to a Lagrangian density, so there's no problem defining it on something noncompact (and no need to integrate).}
 \pavel{A bit confused about the new Remark 1.59, need to discuss.}
 \item Page 34 point 1: The intended map here was the pullback along $\mr{Re} \colon V \to V_\RR$, corrected here. \chris{Todo, respond to the other part.}
 \item Page 34 point 2: The parameter $\eps$ in the given equivalence corresponds to $\d z$, where $z$ is a complex coordinate on the factor $\CC$.  Because this parameter has degree 1, it is formal and the issue indicated here does not arise.
 \item Page 35: Added some clarification to the notation here.
 \item Page 36: Yes, $Q_i$ and $\lambda$ are sections of the same thing, clarified this point. \chris{rest to respond to}
 \item Page 37: Added a clarifying sentence to the beginning of Section 2.1 about Euclidean signature. \brian{Todo: non associative stuff.} \pavel{I don't think we should mention Euclidean signature in the beginning of Section 2.1 (we are talking about complex vector spaces there).}
 \item Page 38:
 \item Page 51: Thank you, reference added.
 \item Page 52: \chris{I talked to Brian about this, I'm not totally sure that I understand the objection.  Maybe the point is that the twisted theory can still admit real forms that could be thought of as twists of a real form of the supersymmetric theory, even if the corresponding real form didn't include a square-zero supercharge?} 
 \pavel{I've added Lagrangian = maximal isotropic}
 \item Page 54: Added a reference for this claim to the relevant section of [ES].
 \item Page 56: This section was written confusingly, and we have corrected it.  Both $Q_+$ and $Q_-$ individually have stabilizers isomorphic to $\mr{SU}(4)$, and the intersection of these stabilizers is isomorphic to $\mr{SU}(3)$.
 \item Page 77: Thanks, we have corrected the confusing appearance of ``six-dimensional'' which refers to the spin group of the 6-dimensional vector space, rather than the dimension of the spin representation which is 4.
\end{enumerate}
